HEP Software Foundation Community White Paper Working Group -- Data Analysis and Interpretation

### 2018-02-15 CWP/papers/HSF-CWP-2017-05_analysis/latex/cwp-wg-analysis-interpretation.tex
updates to affiliations

\author{HEP Software Foundation:}
\author[1]{Riccardo Maria Bianchi}
\author[2]{Brian Bockelman}
\author[3]{Nuno Castro}
\author[4]{Peter Elmer}
\author[16]{Robert Gardner}
\author[14]{Maria Girone}
\author[5]{Oliver Gutsche}
\author[14]{Benedikt Hegner}
\author[6]{Jos\'{e} M. Hern\'{a}ndez}
\author[5]{Bodhitha Jayatilaka}
\author[4]{David Lange}
\author[7]{Mark Neubauer}
\author[7]{Daniel S. Katz}
\author[8]{Lukasz Kreczko}
\author[9]{James Letts}
\author[10]{Shawn McKee}
\author[11]{Christoph Paus}
\author[5]{Kevin Pedro}
\author[12]{Eduardo Rodrigues}
\author[8]{Tai Sakuma}
\author[5]{Elizabeth Sexton-Kennedy}
\author[13]{Michael D. Sokoloff}
\author[9]{Frank W\"{u}rthwein}
\author[15]{Carl Vuosalo}

\affiliation[1]{University of Pittsburgh}
\affiliation[2]{University of Nebraska-Lincoln}
\affiliation[3]{LIP and University of Minho, Supported by FCT-Portugal, IF/00050/2013/CP1172/CT0002}
\affiliation[4]{Princeton University}
\affiliation[5]{Fermi National Accelerator Laboratory, Supported by the US-DOE, DE-AC02-07CH11359}
\affiliation[6]{CIEMAT, Supported by ES-MINECO, FPA2016-80994-c2-1-R and MDM-2015-0509}
\affiliation[7]{University of Illinois Urbana-Champaign}
\affiliation[8]{University of Bristol}
\affiliation[9]{UC San Diego}
\affiliation[10]{University of Michigan, Supported by the US-DOE, DE-SC0007859 and US-NSF, 76749/1136652/2}
\affiliation[11]{Massachusetts Institute of Technology}
\affiliation[12]{University of Cincinnati, Supported by the US-NSF, ACI-1450319}
\affiliation[13]{University of Cincinnati, Supported by the US-NSF, ACI-1558219}
\affiliation[14]{CERN}
\affiliation[15]{University of Wisconsin-Madison}
\affiliation[16]{University of Chicago}

>>>>

\author{HEP Software Foundation:}
\author[a]{Riccardo Maria Bianchi}
\author[b]{Brian Bockelman}
\author[c,d]{Nuno Castro}
\author[e]{Peter Elmer}
\author[f]{Robert Gardner}
\author[g]{Maria Girone}
\author[h,1]{Oliver Gutsche}
\author[g]{Benedikt Hegner}
\author[i]{Jos\'{e} M. Hern\'{a}ndez}
\author[h]{Bodhitha Jayatilaka}
\author[e]{David Lange}
\author[j,1]{Mark Neubauer}
\author[j]{Daniel S. Katz}
\author[k]{Lukasz Kreczko}
\author[l]{James Letts}
\author[m]{Shawn McKee}
\author[n]{Christoph Paus}
\author[h]{Kevin Pedro}
\author[o]{Eduardo Rodrigues}
\author[k]{Tai Sakuma}
\author[h]{Elizabeth Sexton-Kennedy}
\author[o]{Michael D. Sokoloff}
\author[l]{Frank W\"{u}rthwein}
\author[p]{Carl Vuosalo}

\affiliation[a]{University of Pittsburgh, Pittsburgh, Pennsylvania, USA}
\affiliation[b]{University of Nebraska-Lincoln, Lincoln, Nebraska, USA}
\affiliation[c]{Laboratório de Instrumentação e Física Experimental de Partículas, Lisbon, Portugal}
\affiliation[d]{University of Minho, Braga, Portugal}
\affiliation[e]{Princeton University, Princeton, New Jersey, USA}
\affiliation[f]{University of Chicago, Chicago, Illinois, USA}
\affiliation[g]{CERN, Geneva, Switzerland}
\affiliation[h]{Fermi National Accelerator Laboratory, Batavia, Illinois USA}
\affiliation[i]{Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas, Madrid, Spain}
\affiliation[j]{University of Illinois at Urbana-Champaign, Urbana, Illinois USA}
\affiliation[k]{University of Bristol, Bristol, UK}
\affiliation[l]{University of California at San Diego, La Jolla, California, USA}
\affiliation[m]{University of Michigan, Ann Arbor, Michigan, USA}
\affiliation[n]{Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
\affiliation[o]{University of Cincinnati, Cincinnati, Ohio, USA}
\affiliation[p]{University of Wisconsin-Madison, Madison, Wisconsin, USA}
\affiliation[1]{Paper Editor}

%\affiliation[c]{Laboratório de Instrumentação e Física Experimental de Partículas, Lisbon, Portugal and University of Minho, Braga, Portugal, Supported by FCT-Portugal, IF/00050/2013/CP1172/CT0002}
%\affiliation[g]{Fermi National Accelerator Laboratory, Batavia, Illinois USA, Supported by the US-DOE, DE-AC02-07CH11359}
%\affiliation[h]{Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas (CIEMAT), Madrid, Spain, Supported by ES-MINECO, FPA2016-80994-c2-1-R and MDM-2015-0509}
%\affiliation[i]{University of Illinois at Urbana-Champaign, Urbana, Illinois USA, Supported by the US-DOE, DE-SC0018098 and US-NSF ACI-1558233}
%\affiliation[m]{University of Michigan, Supported by the US-DOE, DE-SC0007859 and US-NSF, 76749/1136652/2}
%\affiliation[o]{University of Cincinnati, Supported by the US-NSF, ACI-1450319}
%\affiliation[p]{University of Cincinnati, Supported by the US-NSF, ACI-1558219}
